Measuring Perceptions and Preferences for Meritocracy

### 2021-09-02 paper.Rmd
update
- check chunks
- render paper en html OK

```{r table-indicadores, echo=FALSE}
pacman::p_load(knitr, kableExtra, dplyr)

tabitems <- read.csv(file = "input/tables/table01.csv",header = 1,sep = ",",encoding = "UTF-8") # call file generated externally for the table
cnames <- c("Component", "Dimensions","Item (english)" , "Item original (spanish)")
cap <- "Items of the perceptions and preferences for meritocracy scale."

@@

```{r corpoly, echo=FALSE, fig.cap = "Perceptions & preferences for meritcoracy items' polychoric correlations", fig.align='center'}
load(file = "input/data/proc/data_s2.RData")

# generate polychoric matrix
cor_s2<- data_s2 %>% select(perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw) %>% lavaan::lavCor(., ordered=names(.))

@@

```{r tab-loads, echo=FALSE, eval=FALSE}
pacman::p_load(dplyr)
load(file = "output/tables/tb.fm.RData")
cap <- "Factor loads and model fit."
tb.col  <- c("Variables",1:4,1:4,1:4)
tb.caption <- "Factor loadings and fit measures"
tb.foot <- paste0("Standardized factor loadings using DWLS estimator ; CFI = Comparative fit index (scaled); RMSEA = Root mean square error of approximation (scaled)")
tb.fm <- tb.fm %>%
    mutate(vars = recode(vars,
                         "A. Who the more they try they manage to get bigger rewards that those who strive less."= "Perception Effort",
                         "B. Who possess more talent they manage to obtain greater rewards than those who possess less talent."= "Perception Talent",
                         "C. Who they have rich parents manage to get out ahead."="Perception rich parents",
                         "D. Who they have good contacts they manage to get out ahead."="Perception contacts",
                         "E. Who the more they try they should get greater rewards than those who they try less." = "Preferences Effort",
                         "F. Who possess more talent they should get greater rewards than those who possess less talent."= "Preferences Talent",
                         "G. It's fine that those who have rich parents get ahead" ="Preferences rich parents",
                         "H. Is well that those who have good contacts get ahead." = "Preferences contacts"))
tb.fm01<- kable(tb.fm, format = table_format, booktabs = T,linesep = "", escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = cap) %>%
          kable_styling(full_width = table_format2,latex_options = c("hold_position","scale_down"), position = "center",font_size = 9) %>%
#          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>%
#          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>%
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12))  %>%
          footnote(general = tb.foot,threeparttable = T);tb.fm01
```

@@

```{r fcloads-inv, echo=FALSE}
table_format = if(knitr::is_html_output()) { #conditional instructions for kable
  "html" #if html set "html" in format
} else if(knitr::is_latex_output()) {
  "latex"#if latex set "latex" in format
}
table_format2 = if(knitr::is_html_output()) {
  T
} else if(knitr::is_latex_output()) {
  F
}
# Note: 
# This CFA corresponds to the sample from the Factorial Survey Study 
load(file = "input/data/proc/data_s3_inv.RData") #load data study 3
fs01  <- data_s3_inv %>% dplyr::filter(dataset=="fsw02") #subset sample

@@

for (i in names(loads01)) {
  # tb.load[,i] <- sjlabelled::as_character(tb.load[,i])
  loads01[,i] <- sprintf(loads01[,i], fmt = '%#.3f')
}
loads01[loads01=="NA"] <- ""

@@

#------ merge ------#
tb.fm2<- bind_rows(loads01,fm.df)
tb.fm2<- tb.fm2 %>% 
  mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>%
  select(vars,everything())
# load(file = "output/tables/tb.fact-f02.RData")
tb.col  <- c(" ",
             "Meritocratic","Non-meritocratic",
             "Meritocratic","Non-meritocratic")
tb.caption <- "Factor loadings and fit measures for the second sample for study 3" 
tb.foot <- paste0("Standardized factor loadings using DWLS estimator ; CFI = Comparative fit index (scaled); RMSEA = Root mean square error of approximation (scaled)")
tb.fm02<- kable(tb.fm2,escape = FALSE,align = "lcccc",col.names = tb.col, caption = tb.caption, booktabs = T,linesep = "",format = table_format) %>%
          kable_styling(full_width = table_format2,
                        latex_options = c("hold_position"), 
                        position = "center",
                        font_size = 12,
                        bootstrap_options = c("striped", "bordered")) %>%
          add_header_above(header = c(" "=1,"Perception"= 2,"Preference"= 2)) %>%
          add_header_above(header = c(" "=1,"Factor loadings"= 4)) %>%
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>%
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm02
```

>>>>

```{r table-indicadores, echo=FALSE}
pacman::p_load(knitr, kableExtra, dplyr)
table_format = if(knitr::is_html_output()) { #conditional instructions for kable
  "html" #if html set "html" in format
} else if(knitr::is_latex_output()) {
  "latex"#if latex set "latex" in format
}
tabitems <- read.csv(file = "input/tables/table01.csv",header = 1,sep = ",",encoding = "UTF-8") # call file generated externally for the table
cnames <- c("Component", "Dimensions","Item (english)" , "Item original (spanish)")
cap <- "Items of the perceptions and preferences for meritocracy scale."

@@

```{r corpoly, echo=FALSE, fig.cap = "Perceptions & preferences for meritcoracy items' polychoric correlations", fig.align='center'}
load(file = "input/data/proc/data_s2.RData")
pacman::p_load(dplyr)
# generate polychoric matrix
cor_s2<- data_s2 %>% dplyr::select(perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw) %>% lavaan::lavCor(., ordered=names(.))

@@

@@

```{r fcloads-inv, echo=FALSE}
table_format = if(knitr::is_html_output()) { #conditional instructions for kable
  "html" #if html set "html" in format
} else if(knitr::is_latex_output()) {
  "latex"#if latex set "latex" in format
}
table_format2 = if(knitr::is_html_output()) {
  T
} else if(knitr::is_latex_output()) {
  F
}
# Note: 
# This CFA corresponds to the sample from the Factorial Survey Study 
load(file = "input/data/proc/data_s3_inv.RData") #load data study 3
pacman::p_load(dplyr,knitr,kableExtra)
fs01  <- data_s3_inv %>% dplyr::filter(dataset=="fsw02") #subset sample

@@

for (i in names(loads01)) {
  loads01[,i] <- sprintf(loads01[,i], fmt = '%#.3f')
}
loads01[loads01=="NA"] <- ""

@@

#------ merge ------#
tb.fm2<- bind_rows(loads01,fm.df)
tb.fm2<- tb.fm2 %>% 
  mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>%
  select(vars,everything())
tb.col  <- c(" ",
             "Meritocratic","Non-meritocratic",
             "Meritocratic","Non-meritocratic")
tb.caption <- "Factor loadings and fit measures for the second sample for study 3" 
tb.foot <- paste0("Standardized factor loadings using DWLS estimator ; CFI = Comparative fit index (scaled); RMSEA = Root mean square error of approximation (scaled)")
tb.fm02<- kable(tb.fm2,escape = FALSE,align = "lcccc",col.names = tb.col, caption = tb.caption, booktabs = T,linesep = "",format = table_format) %>%
          kable_styling(full_width = table_format2,
                        latex_options = c("hold_position"), 
                        position = "center",
                        font_size = 12,
                        bootstrap_options = c("striped", "bordered")) %>%
          add_header_above(header = c(" "=1,"Perception"= 2,"Preference"= 2)) %>%
          add_header_above(header = c(" "=1,"Factor loadings"= 4)) %>%
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>%
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm02
```
